The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2022-01-30 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd
Discussion on why away teams more affected than home teams

@@

At least some of that improvement from away teams came from significantly higher
two-point efficiency. This corresponds with the conclusion from @Harris,
where they found home teams are best suited to capitalize on advantages from two-point
shots. Normally, by shooting more two-pointers themselves and forcing away teams to
shoot more two-pointers the home team benefits from increasing effects of
home-court advantage. However, with away teams significantly improving two-point
shooting in the bubble this strategy was no longer viable and home-court
advantage disappeared.

>>>>

At least some of that improvement from away teams came from significantly higher
two-point efficiency. This corresponds with the conclusion from \citet{Harris},
where they found home teams are best suited to capitalize on advantages from two-point
shots. Normally, by shooting more two-pointers themselves and forcing away teams to
shoot more two-pointers the home team benefits from increasing effects of
home-court advantage. However, with away teams significantly improving two-point
shooting in the bubble this strategy was no longer viable and home-court
advantage disappeared.

@@

It's worth noting that much of this paper discussed the the effects from an
offensive point of view, focusing on a teams ability to score. However, one 
of the main factors that influence an offense's ability to score is the opposing
defense. It's possible that home court advantage mainly functions as an extra defender
for home teams, which is how it negatively impacts away scoring. There is not much
home fans can do to help their team on offense, except being quiet so players can 
easily communicate and focus. However, when on defense fans can support their team
by cheering loudly and making it harder on the offense. This would explain how away 
teams were able to improve offensively in the bubble. Home teams did not have the 
regular help from the noise of fans that hinder the away team's offensive efforts. 
This would also explain why home team offense didn't show significant change in the 
bubble, the in-game offensive environment was largely unaltered for home teams
since the bubble provided the same quiet environment they're used to at home while
on offense. Meanwhile, removing the "sixth defender" from home team defensive efforts 
allowed away teams to work more effectively on offense.

An interesting finding is all shooting and scoring numbers for both home and
away teams did make at least small increases. Although these increases
were not all significant these increases are exactly what is reported in
@Carron2005 when they explain how evidence suggests that teams perform
better with the absence of fans. This is important because it coincides with our
conclusion that home-court advantage mostly plays into games by negatively impacting away
teams by acting as an extra defender. If fans cause overall performance to drop, then home 
court advantage must come from a bigger drop in away performance than the drop in home
performance. This is why away teams were able to close the gap with home teams with
home-court advantage removed.
